My title

### 2024-10-24 paper/paper.qmd
Add Result and Discussion parts; Modify Appendix B

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Yongqi Liu
  - Yuxuan Wei
thanks: "Code and data are available at: [https://github.com/wyx827/2024USpresidentialelection.git]."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#install.packages("tidymodels")
library(tidyverse)
library(ggplot2)
analysis_data <- read_csv(here::here("data/02-analysis_data/cleaned_US_voting.csv"))
```

@@

We use the statistical programming language R [@citeR].... Following @tellingstories, we consider...

Overview text

## Measurement

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

@@

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (fig-bills),

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

Talk more about it.

And also planes (fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

Talk way more about it.

@@

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

@@

To model Donald Trump’s polling percentages over time, we employed a Bayesian linear regression framework. Bayesian methods provide a flexible approach to inference by incorporating prior beliefs and updating them with observed data, allowing us to quantify uncertainty in both parameter estimates and predictions.

Here we briefly describe the Bayesian model used to investigate the winning probability of Trump. Background details and diagnostics are included in [Appendix @sec-model-details].

@@

The model takes the form:
The model takes the form:

## Interpretation of Coefficients:

@@

## Interpretation
The posterior distributions of the parameters allow us to quantify the uncertainty around each effect:
- The coefficient for end_date informs us about how Trump’s polling percentages have evolved over time. A positive coefficient would suggest an upward trend, while a negative coefficient would indicate a decline.
- The coefficient for numeric_grade captures the impact of pollster quality on the polling percentage. High-quality pollsters may produce different estimates compared to lower-quality ones.
- The state-level effects account for regional differences in Trump’s support. Some states may show significantly higher or lower levels of support, even after adjusting for the time of the poll and pollster quality.

@@

# Diagnostic plots for the model
```{r}
#| echno: false
#| label: fig-diagnosis
#| tbl-cap: Linear Regression Assumptions hold.
#| echo: false
#| warning: false
#| message: false

@@

```{r}
library(car)
vif(regression_model)
```

```{r}
summary(regression_model)
```

## Model justification

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Xuanle Zhou
  - Yongqi Liu
  - Yuxuan Wei
thanks: "Code and data are available at: [https://github.com/wyx827/2024USpresidentialelection.git]."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

#install.packages("tidymodels")

library(tidyverse)
library(ggplot2)
library(rstanarm)
library(knitr)

analysis_data <- read_csv(here::here("data/02-analysis_data/cleaned_US_voting.csv"))
```

@@

This study uses R packages [@citeR] to clean and analyz the dataset , including libraries from tidyverse [], ggplot2[].

After cleaning the data, which included grouping and removing missing values, the analysis dataset consists of 1,683 observations, focusing on the following 11 variables: pollster name, methodology, numeric grade, start date, end date, sample size, candidate name, percentage, transparency score, and population group.

## Data Measurement and Considerations

The dataset for this analysis is sourced from FiveThirtyEight, which rigorously collects and aggregates polling data from a variety of firms to reflect public opinion. To ensure the integrity of the data, only polls that adhere to specific criteria are included in the dataset. Each poll must provide essential information, such as the pollster’s name, survey dates, sample sizes, and methodological details (e.g., polling medium, voter files, weighting criteria). Polls that are deemed nonscientific, that blend data from multiple sources, or that are conducted by hobbyists are excluded.

Once a poll meets these stringent standards, it is incorporated into the database, enabling it to inform polling averages, forecasts, and political coverage. This careful selection process ensures that the dataset accurately captures and reflects the nuances of public sentiment and behavior.

@@

The outcome variable of interest for this research is the percentage, representing the level of public support for Donald Trump. The distribution in @fig-pct indicates that most observations cluster around a support percentage of approximately 48%, suggesting moderate backing from the electorate. Additionally, a smaller proportion of polls show support exceeding 55%, indicating that while Trump has a core base, many voters remain either indifferent or opposed to him.

```{r}
#| label: fig-pct
#| fig-cap: Distribution of Support (percent) for Donald Trump
#| echo: false
#| warning: false
#| message: false
ggplot(analysis_data, aes(x = percent)) +
  geom_histogram(binwidth = 2, fill = "green", color = "black", alpha = 0.7) +
  labs(title = "Distribution of Support (percent) for Donald Trump", x = "Support Percentage (percent)", y = "Count") +
  theme_minimal()
```

@@

### Numeric Grade

The numeric grade reflects the quality of the pollster, with FiveThirtyEight defining a scale from 0 to 3. A grade of 0 indicates a low-quality poll, while a grade of 3 signifies a high-quality pollster. After filtering for pollsters with a numeric grade higher than 2.5, we identified a total of 30 distinct pollsters, with half of them scoring between 2.6 and 2.8, as shown in @fig-numeric-grade .

```{r}
#| label: fig-numeric-grade
#| fig-cap: Distribution of Numeric Grades (2.6 to 3.0)
#| echo: false
#| warning: false
#| message: false

summary_data <- analysis_data %>%
    distinct(pollster_rating_name, .keep_all = TRUE) %>%
    group_by(numeric_grade) %>%
    summarise(count = n())

ggplot(analysis_data %>% distinct(pollster_rating_name, .keep_all = TRUE), 
       aes(x = numeric_grade)) + 
    geom_histogram(binwidth = 0.1, fill = "green", color = "black", alpha = 0.7) + 
    scale_x_continuous(breaks = seq(2.5, 3.0, by = 0.1)) + 
    scale_y_continuous(breaks = seq(0, max(summary_data$count), by = 1)) + 
    labs(title = "Distribution of Numeric Grades (2.6 to 3.0)", 
         x = "Numeric Grade", 
         y = "Count of Distinct Polls") + 
    theme_minimal()
```
### Sample Size

The sample size indicates the number of respondents in each poll. The distribution in @fig-sample-size exhibits a right-skewed shape, suggesting that there are more observations with smaller sample sizes compared to larger ones. The peak of the distribution is around 1,000, indicating that this is the most common sample size used in the polls. Overall, the sample size data highlights that each poll contains a sufficient number of respondents to provide reliable insights.

```{r}
#| label: fig-sample-size
#| fig-cap: Distribution of Sample Size
#| echo: false
#| warning: false
#| message: false

ggplot(analysis_data %>% filter(sample_size < 3000), aes(x = sample_size)) +
  geom_histogram(binwidth = 100, fill = "green", color = "black", alpha = 0.7) +
  labs(title = "Distribution of Sample Size", x = "Sample Size", y = "Count") +
  theme_minimal()
```
### Transparency Score

The Transparency Score measures how transparent a pollster is, calculated based on the amount of information disclosed about its polls, weighted by recency. The highest possible score is 10, while the lowest is 0. The distribution of Transparency Scores for the filtered pollsters shows a peak around 9 as presented in @fig-transparency-score, indicating that this is the most common score. This suggests that among the selected pollsters, there is a predominance of high transparency scores.

```{r}
#| label: fig-transparency-score
#| fig-cap: Distribution of Transparency Score
#| echo: false
#| warning: false
#| message: false

ggplot(analysis_data %>% 
         distinct(pollster_rating_name, .keep_all = TRUE), 
       aes(x = transparency_score)) + 
  geom_histogram(binwidth = 1, fill = "green", color = "black", alpha = 0.7) + 
  scale_x_continuous(breaks = 3:10) +
  scale_y_continuous(breaks = seq(0, max(summary_data$count), by = 1)) +  
  labs(title = "Distribution of Transparency Score", x = "Transparency Score", y = "Count of Distinct Polls") + 
  theme_minimal()
```

### end date

The end date indicates when each poll concluded. @fig-end-date shows that as the final result of the U.S. election approached, more polls were conducted and completed. This trend reflects an increased interest in capturing public opinion and predicting electoral outcomes as election day neared, emphasizing the significance of real-time sentiment analysis during this critical period.

```{r}
#| label: fig-end-date
#| fig-cap: Distribution of End Dates
#| echo: false
#| warning: false
#| message: false

ggplot(analysis_data, aes(x = as.Date(end_date))) + 
  geom_line(stat = "count", color = "black", size = 1) + 
  labs(title = "Distribution of End Dates", x = "End Date", y = "Count") + 
  theme_minimal()
```

@@

To model Donald Trump’s polling percentages over time, we employed a multiple linear regression framework. This approach estimates the relationship between polling percentages and various predictors by fitting a linear equation to the data. By analyzing the coefficients, we can quantify the impact of each predictor on Trump’s polling percentages, while also assessing the overall fit of the model and making predictions based on the observed trends.

Here we briefly describe the multiple linear regression model used to investigate the winning probability of Trump. Background details and diagnostics are included in [Appendix -@sec-model-details].

@@

The model takes the form:

\begin{align}
\text{pct}_i &= \beta_0 + \beta_1 \cdot \text{numeric\_grade}_i + \beta_2 \cdot \text{transparency\_score}_i \\
             &\quad + \beta_3 \cdot \text{sample\_size}_i + \beta_4 \cdot \text{state}_i + \beta_5 \cdot \text{end\_date}_i + \epsilon_i \\
\epsilon_i &\sim \text{Normal}(0, \sigma^2)
\end{align}

Where: 
\begin{align}
\beta_0 & \text{ is the intercept term} \\
\beta_1, \beta_2, \beta_3, \beta_4, \beta_5 & \text{ are the coefficients for each predictor} \\
\sigma^2 & \text{ is the variance of the error term}
\end{align}

# Interpretation of Coefficients:

@@

## Interpretation

The posterior distributions of the parameters allow us to quantify the uncertainty around each effect:\

* The coefficient for end_date informs us about how Trump’s polling percentages have evolved over time. A positive coefficient would suggest an upward trend, while a negative coefficient would indicate a decline.\
* The coefficient for numeric_grade captures the impact of pollster quality on the polling percentage. High-quality pollsters may produce different estimates compared to lower-quality ones.\
* The state-level effects account for regional differences in Trump’s support. Some states may show significantly higher or lower levels of support, even after adjusting for the time of the poll and pollster quality.

@@

# Diagnostic plots for the model
```{r}
#| echno: false
#| label: fig-diagnosis-1
#| tbl-cap: Linear Regression Assumptions hold.
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| echno: false
#| label: fig-diagnosis-2
#| tbl-cap: Linear Regression Assumptions hold.
#| echo: false
#| warning: false
#| message: false

#library(car)
#vif(regression_model)
```

### Model justification
